---
title: "exercise_2_2"
author: "Lindsey Greenhill"
date: "2/3/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
```

## Problem 2a. Page 27 of textbook

```{r data, echo=FALSE}
births <- tibble(prop_girls = 
                   c(.4777,
                     .4875,
                     .4859,
                     .4754,
                     .4874,
                     .4864,
                     .4813,
                     .4787,
                     .4895,
                     .4797,
                     .4876,
                     .4859, .4857, .4907, .5010, .4903, .4860, .4911, .4871, .4725, .4822, .4870, .4823, .4973))

```


```{r 2a, echo=FALSE}

# calculating standard deviation

sd_actual <- sd(births$prop_girls)

# averaging the proportions above and dividing by the square root of the sample
# size. So p bar divided by the square root of the number. Dividing by 24
# because we have 24 data points so that is our sample size.

avg_birth <- mean(births$prop_girls)

std_theoretical <- sqrt(avg_birth * (1 - avg_birth) / 3900)
```

## Problem 2b

```{r 2a}
# use the chi-squared test to do this with 23 df. Finding the upper and lower bound and seeing if the chi squared test above is within these bounds. 

# finding the chi sq test statistic 

chisq <- ((23) * sd_actual^2) / std_theoretical^2

# not really sure what the stuff below is for?

lower_bound <- qchisq(.05/2, df = 23)
upper_bound <- qchisq(.975, df = 23)

# calculating the p value 

p_val <- 2*pchisq(chisq, df = 23)

# calculating confidence interval

upper_real <- sqrt(23*24^2 / lower_bound)
lower_real <- sqrt(23*24^2 / upper_bound)

```

The chi-squared statistic is *`r chisq`*. This value falls within the calculated lower and upper bounds of *`r lower_bound`, `r upper_bound`* and is thus not statistically significant. 


## Problem 3

```{r 3a}

# creating vector for random draws

sums <- rep(NA, 1000)

for(i in 1:1000){
  
  # 20 random numbers between 0 and 1
  
  noms <- runif(20, 0, 1)
  
  # sum of the random draws
  
  noms_sum <- sum(noms)
  
  sums[i] <- noms_sum
}

# plotting a histogram

# getting the mean of 

{
hist(sums, main = "Distribution of 1000 Sims of Draws(0,1)",
     probability = TRUE, las = 1)
curve(dnorm(x=x, mean = mean(sums), sd = sd(sums)),
      col = "steelblue2", lwd = 2, add  = TRUE, yaxt = "n")
}

```

write paragraph saying that it is not exactly the same, demonstrated in the mean not being exactly ten. Can be explained by the fact that this is just simulations, the world is not perfect. 

